Profile likelihoods for geostatsistical models using GPU's

### 2022-01-10 pkg/oldgpuRandom/inst/doc/L2021_11/paper2.Rnw
paper 2
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@3106 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

<<swiss_profile_many,echo = FALSE, eval=TRUE, cache=TRUE, fig.width=4,fig.height=3, fig.show ="hold", fig.align='center', fig.cap = "profile LogL of slope parameter", out.width = "50%",dev='pdf',fig.pos="H">>=
setwd("/home/ruoyong/diseasemapping/pkg/oldgpuRandom/inst/doc/L2021_11")
knitr::include_graphics(c('profile_logl_swiss.png','betaprofile.png'))
@

>>>>

<<swiss_profile_many,echo = FALSE, eval=TRUE, cache=TRUE, fig.width=4,fig.height=3, fig.show ="hold", fig.align='center', fig.cap = "profile LogL of slope parameter", out.width = "33%",dev='pdf',fig.pos="H">>=
#setwd("/home/ruoyong/diseasemapping/pkg/oldgpuRandom/inst/doc/L2021_11")
setwd("/home/ruoyong/L2021_11")
knitr::include_graphics(c('profile_logl_swiss.png','betaprofile.png','varprofile.png'))
@
